### 2022-03-01 src/text/1-introduction.tex
Run pre-commit
Run tex indentation

Moreover, the operation of CTA as an observatory introduces the necessity of sharing
its data publicly. The data-reduction workflow of different IACTs of the current
generation is remarkably similar, resulting in a ``high'' data level that can be
finally used to derive scientific results (e.g. spectra, sky maps, light curves).
The information in this high data level is independent on the data reduction,
and eventually of the detection technique. This implies, for example, that data
from IACT and WCD can be represented within the same model.
The efforts to prototype the future CTA data model and to convert current IACT
data in a format usable with the newly-available science tools converged in the 
so-called ``Data Format for Gamma-ray Astronomy'' initiative
\citep{gadf_proc, gadf_universe}, abbreviated in \texttt{gamma-astro-data-format}
(GADF). The latter proposes prototypical specifications to produce files based
on the flexible image transport system (FITS) format \citep{fits} encapsulating
this high-level information. This is realized by storing a list of gamma-like
events with their measured quantites (energy, direction, arrival time) and a
parametrisation of the response of the system (see Sec.~\ref{ssec:gammapy-data}
and Sec.~\ref{ssec:gammapy-irf} for more information).

@@

Astronomical data analysis software written in Python existed since 2000. e.g.,
sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
\citep{pyfact}.

@@

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth, angle=270]{static/gammapy-big-picture}
	\caption{
		Gammapy is a Python package for high-level gamma-ray data analysis. Using event
		lists, exposures and point spread functions as input you can use it to generate
		science results such as images, spectra, light curves or source catalogs. So
		far it has been used to simulate and analyse H.E.S.S., CTA and
		\textit{Fermi}-LAT data, hopefully it will also be applied to e.g., VERITAS,
		MAGIC or HAWC data in the future.
	}
	\label{fig:big-picture}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
	\caption{
		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
		solid arrows, optional dependencies (the rest) with dashed arrows.
	}
	\label{fig:dependencies}
\end{figure}

>>>>

Moreover, the operation of CTA as an observatory introduces the necessity of
sharing its data publicly. The data-reduction workflow of different IACTs of
the current generation is remarkably similar, resulting in a \textit{high} data
level that can be finally used to derive scientific results (, spectra, sky
maps, light curves). The information in this high data level is independent on
the data reduction, and eventually of the detection technique. This implies,
for example, that data from IACT and WCD can be represented within the same
model. The efforts to prototype the future CTA data model and to convert
current IACT data in a format usable with the newly-available science tools
converged in the so-called \textit{Data Format for Gamma-ray Astronomy}
initiative~\citep{gadf_proc, gadf_universe}, abbreviated in
\texttt{gamma-astro-data-format} (GADF). The latter proposes prototypical
specifications to produce files based on the flexible image transport system
(FITS) format~\citep{fits} encapsulating this high-level information. This is
realized by storing a list of gamma-like events with their measured quantites
(energy, direction, arrival time) and a parametrisation of the response of the
system (see Sec.~\ref{ssec:gammapy-data} and Sec.~\ref{ssec:gammapy-irf} for
more information).

@@

Astronomical data analysis software written in Python existed since 2000. e.g.,
sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
~\citep{pyfact}.

@@

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth,
		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
		for high-level gamma-ray data analysis. Using event lists, exposures and point
		spread functions as input you can use it to generate science results such as
		images, spectra, light curves or source catalogs. So far it has been used to
		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
		will also be applied to e.g. VERITAS, MAGIC or HAWC data in the future. }
	\label{fig:big-picture}

\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
	\caption{
		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
		solid arrows, optional dependencies (the rest) with dashed arrows. }
	\label{fig:dependencies}

\end{figure}

### 2022-03-01 src/text/2-package-subsections/modeling.tex
Run pre-commit
Run tex indentation

The models are grouped into the following categories:
\begin{itemize}
\item SpectralModel: models to describe spectral shapes of sources
\item SpatialModel: models to describe spatial shapes (morphologies) of sources
\item TemporalModel: models to describe temporal flux evolution of sources, such as light and phase curves
\end{itemize}
The models follow a naming scheme which contains the category as a suffix to the class name.

@@

The model gallery provides a visual overview of the available models in Gammapy.
Most of the analytic models  commonly used in gamma-ray astronomy are built-in. We also offer a wrapper to radiative models implemented in the Naima package \cite{naima}. The modeling framework can be easily extended with user-defined models. For example agnpy models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \citep[see section3.5 of ][]{2021arXiv211214573N} .

@@

The Fit class provides a uniform interface to multiple fitting backends: “minuit” \citep{iminuit}, “scipy”, \citep{2020SciPy-NMeth}, and “sherpa” \citep{sherpa-2005,sherpa-2011}.
Note that, for now, covariance matrix and errors are computed only for the fitting with MINUIT. However depending on the problem other optimizers can better perform, so sometimes it can be useful to run a pre-fit with alternative optimization methods.
In future we plan to extend the supported Fit backend, including for example MCMC solutions.  \footnote{a prototype is available in gammapy-recipes, \url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}

>>>>

The models are grouped into the following categories:

\begin{itemize}
	\item SpectralModel: models to describe spectral shapes of sources
	\item SpatialModel: models to describe spatial shapes (morphologies) of sources
	\item TemporalModel: models to describe temporal flux evolution of sources, such as
	      light and phase curves

\end{itemize}

The models follow a naming scheme which contains the category as a suffix to
the class name.

@@

The model gallery provides a visual overview of the available models in
Gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\cite{naima}. The modeling framework can be easily extended with
user-defined models. For example agnpy models that describe leptonic radiative
processes in jetted Active Galactic Nuclei (AGN) can wrapped into
gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .

@@

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported Fit backend, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,

	\url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}
